---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: ref.bib
link-citations: yes
urlcolor: blue
linkcolor: blue
fontsize: 11pt
geometry: margin = 1.2in
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{multirow}
- \usepackage[labelfont=bf]{caption}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{algorithm}
- \usepackage[noend]{algpseudocode}
- \makeatletter
- \def\BState{\State\hskip-\ALG@thistlm}
- \makeatother
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

\pagenumbering{gobble}

```{r child = 'titlepage.Rmd'}
```

\newpage

```{r child = 'declaration.Rmd'}
```

\newpage
\pagestyle{fancy}

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{roman}

\fancyhead[CO,CE]{Abstract}
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

```{r child = 'Abstract.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Acknowledgements}
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

```{r child = 'acknowledgements.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Table of Contents}
\setcounter{tocdepth}{2}
\tableofcontents

\newpage
\fancyhead[CO,CE]{List of Figures and Tables}
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\addcontentsline{toc}{section}{List of Tables}
\listoftables


\newpage
\pagenumbering{arabic}

\newpage
\fancyhead[CO,CE]{Introduction}

```{r child = 'chapter1.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Background}

```{r child = 'chapter2.Rmd'}
```


\newpage
\fancyhead[CO,CE]{Existing Approaches}

```{r child = 'chapter3.Rmd'}
```

\newpage
\fancyhead[CO,CE]{SP-FSR Algorithm}

```{r child = 'chapter4.Rmd'}
```


\newpage
\fancyhead[CO,CE]{Experimental Studies}

```{r child = 'chapter5.Rmd'}
```


\newpage
\fancyhead[CO,CE]{Conclusion}

```{r child = 'chapter6.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Appendix I: R Source Codes}
\section*{Appendix I}
\addcontentsline{toc}{section}{Appendix: R Source Codes}

```{r child = 'Appendix2.Rmd'}
```


\FloatBarrier\newpage\fancyhead[CO,CE]{References}

# References
